### 2024-11-08 conteudo/background/linux.tex
create tables of tool
Reviewing background

@@

The Linux kernel is an Unix-like operating system published by Linus Torvalds in 1992 as a free software and
it started becoming popular in late 1990s \citep{linuxbook}. Against popular belief, linux is not a full 
operating system as it do not includes applications such as filesystem utilities, windowing systems. The "Linux" 
distributions know to the public are in fact GNU/Linux operating systems \citep{gnuref}.

The Linux kernel is monolithic organized as a set of subsystem such as process scheduler, memory management, 
device driver infrastruture, networking and filesystems \citep{melissa}.
Each subsystem usually have a maintainer or a group of maintainers, which are people responsible 
for managing and accepting contributions into the subsystem they care of \citep{melissa}.

The contributions to the Linux are coordinate with the usage of the Git source management tool. The contributions 
made to the project are formated as patches, which are text documents describing differences between two different 
versions of a source tree  The patches are sent and reviewed through the Linux mailing lists \citep{melissa}.

Mailing lists are the official means of communication of the Linux community, through the mailing lists the community members 
send and review
contributions to the kernel, discuss topics related to the Linux such as which new features to add, et cetera. 
As there are multiples
subsystems in the Linux kernel, there are multiples mailing lists in the Linux to organize the discussion made. Every subsystem 
have their own mailing list to concentrate the discussion related to the subsystem \citep{melissa}. The iteractions made in the
mailing lists are documented and stored in the Linux kernel Lore \citep{linuxlore}, which serves as a repository of the
discussion made in the Linux kernel to be consulted by anyone interested.

One the the Linux kernel subsystem is the AMD Display Driver, a subsystem responsible for implement the drivers required to enable
AMD GPU's work properly in the Linux environment. The maintainers of this subsystem reported a empirical problem they have in
the subsystem, which is a significant amount of duplicated code in the subsystem, a problem that hinders the maintainment of the
subsystem. This reported problem is the starting point that initiated our research, making the AMD Display Driver our principal
objecte of study to undertand how to mitigate duplicated code in the Linux kernel.

(I WANT TO CHANGE THE AMD DISPLAY paragraph, WHY DO I NEED TO CHANGE IT? I SHOULD ANOTATE WHAT I WANTED, I MADE A CHANGE
 TO MAKE IT BETTER BUT NOT SURE IF THERE IS SOME INFORMATION I WANTED TO PUT IN IT)

>>>>

\todo[inline]{Adicionar um "preambulo" antes da seções do capítulo}

@@

The Linux kernel, a Unix-like operating system kernel, was published by Linus
Torvalds in 1992 as free software. It began gaining popularity in the late
1990s \citep{linuxbook}. Contrary to popular belief, Linux itself is not a
complete operating system, as it lacks components like filesystem utilities and
windowing systems. The so-called ``Linux distributions'' that are commonly
recognized by the public are actually GNU/Linux operating systems, which
include various essential applications alongside the Linux kernel
\citep{gnuref}.

The Linux kernel is monolithic and organized into a set of subsystems, such as
the process scheduler, memory management, device driver infrastructure,
networking, and filesystems \citep{melissa}. Each subsystem typically has a
dedicated maintainer or a team of maintainers responsible for overseeing its
development and managing contributions \citep{melissa}.

Development contributions to the Linux kernel are coordinated using the Git
version control system. These contributions are formatted as patches—text
documents that outline the differences between two versions of the source code.
These patches are then submitted and reviewed via the Linux mailing lists
\citep{melissa}.

Mailing lists are the primary means of communication within the Linux
community. Members of the community use them to submit and review patches,
discuss Linux-related topics, and debate potential new features. Given the
kernel's extensive modularity, each subsystem has its mailing list, allowing
discussions to be organized around specific areas of development
\citep{melissa}. All interactions on these mailing lists are documented and
archived in the Linux Kernel Lore \citep{linuxlore}, which serves as a
repository for kernel discussions and can be accessed by anyone interested.

One of the subsystems within the Linux kernel is the AMD Display Driver, which
is responsible for implementing the drivers needed for AMD GPUs to function
correctly in a Linux environment. The maintainers of this subsystem have
reported a practical issue: a significant amount of duplicated code, which
complicates the maintenance of this subsystem. This problem serves as the
starting point for our research, with the AMD Display Driver as our primary
object of study as we aim to understand and mitigate code duplication in the
Linux kernel. The AMD Display Driver subsystem contains X lines of code, Y
functions/structs, and Z code files, making it a considerable component within
the Linux kernel. Like other subsystems, discussions about the AMD Display
Driver are conducted on its designated mailing list (FIND MAILING LIST AND CITE
HERE).

### 2024-11-08 conteudo/background/nlpsimilarity.tex
Reviewing background

\section{Text similarity detection methods}
\label{sec:similarity}.

The standard methodology for text similarity detection is grounded on building vector embeddings of 
the texts and applying a distance function in these embeddings to measure the similarity between them. 
There are multiple vector embedding methods proposed by the literature, such as bag-of-words, TF-IDF, 
LSI, and Word2Vec \citep{gensimlivro}.
Recent works related to building vector embeddings use Large Language Models (LLM), for example,
the work of Ethayarajh, which uses BERT, ELMo, and GPT \citep{llmsimilar}. 
The most popular distance function used by the literature is the cosine similarity defined by the formula
\citep{cosineref}:

@@

Where $A$ and $B$ are the vector embeddings of the two texts, an advantage of the cosine similarity is that $SC(A,B)$ is
a number between $0$ and $1$, where $SC(A,B)$ values closer to the number $1$ means that two vectors are more similar, 
it is usual to compare the cosine similarity to approximation to a probability value, transforming the values between 
$0$ and $1$ to a percentage between $0 \% $ and $100\%$, through our research, we will use the percentage form.

It is a famous fact that LLM has a high computational cost. An example of the high computational cost is an analysis 
done by Reimers and Gurevych to find the most similar pair in a collection of 10,000 sentences, 
which required about 65 hours with BERT \citep{bertsimilar}. 
We want to compare a similar magnitude of pairs in our work, so we decided not to use LLM for our vector embedding 
method, even though it is a valid solution for smaller codebases.

@@

Gensim is an open-source Python library \citep{gensim} which the owners declare themselves as "The fastest library 
for training of vector embeddings - Python or otherwise. The core algorithms in Gensim use battle-hardened, highly 
optimized and parallelized C routines." \citep{gensimsite}. For the velocity of Gensim, we chose to use this library 
for our vector embedding method.

In this work, we will not explore more alternatives for vector embeddings. We do not want to optimize the
computational cost or the code clone detection to the state of the art as they are not the main objectives 
of our research.

>>>>

\section{Text Similarity Detection Methods}
\label{sec:similarity}

The standard methodology for text similarity detection is based on building
vector embeddings of texts and applying a distance function to these embeddings
to measure the similarity between them. The literature proposes multiple vector
embedding methods, such as bag-of-words, TF-IDF, LSI, and Word2Vec
\citep{gensimlivro}. Recent works related to vector embedding construction
utilize Large Language Models (LLMs), as exemplified by Ethayarajh's work,
which employs BERT, ELMo, and GPT \citep{llmsimilar}. The most popular distance
function used in the literature is cosine similarity, defined by the formula
\citep{cosineref}:

@@

where $A$ and $B$ are the vector embeddings of the two texts. An advantage of
cosine similarity is that $SC(A,B)$ produces a number between $0$ and $1$,
where values closer to $1$ indicate higher similarity. It is common to
interpret cosine similarity as an approximation of probability, transforming
values between $0$ and $1$ into percentages between $0\%$ and $100\%$.
Throughout our research, we will use this percentage form.

It is well-known that LLMs have a high computational cost. For instance, an
analysis by Reimers and Gurevych found that finding the most similar pair in a
collection of 10,000 sentences required about 65 hours with BERT
\citep{bertsimilar}. Since we aim to compare a similar magnitude of pairs in
our work, we decided not to use LLMs for our vector embedding method, even
though they may be suitable for smaller codebases.

@@

Gensim is an open-source Python library \citep{gensim}, which its creators
describe as "The fastest library for training of vector embeddings - Python or
otherwise. The core algorithms in Gensim use battle-hardened, highly optimized,
and parallelized C routines." \citep{gensimsite}. Due to Gensim's speed, we
chose this library for our vector embedding method.

In this work, we do not explore further alternatives for vector embeddings, as
optimizing computational cost or achieving state-of-the-art code clone
detection is not the primary objective of our research.
